Reproducible Research - Peer Assessment 1
========================================================

## STEP1: Loading and preprocessing the data  
Load the data
```{r load data, echo=TRUE}
setwd("E:/Rdir/repdata1")
activity <- read.table(dir()[[1]],
                       sep=",",
                       header=TRUE,
                       stringsAsFactors=FALSE,
                       na.strings="NA")
```

Process/transform the data (if necessary) into a format suitable for your analysis
```{r proc data}
activity$date <- as.Date(activity$date, "%Y-%m-%d")
```

## STEP2:What is mean total number of steps taken per day?  

Make a histogram of the total number of steps taken per day
```{r hist total number, echo=TRUE}
totalstepsperday <- aggregate(steps~date, data=activity, FUN=sum, na.rm=TRUE)
hist(totalstepsperday$steps, xlab="Steps per day", main="Frequency of steps per day")
```

Calculate and report the mean and median total number of steps taken per day
```{r mean median, echo=TRUE}
mean(totalstepsperday$steps)
median(totalstepsperday$steps)
```

## STEP3:What is the average daily activity pattern?  

Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r ts plot interval, echo=TRUE}
stepsperInterval <- aggregate(steps~interval, FUN=mean ,data=activity, na.rm=TRUE)
plot(stepsperInterval$interval, 
     stepsperInterval$steps,
     type="l", 
     xlab="5 Minutes Intervals",
     ylab="Daily Averaged Steps",
     main="Daily Averaged Steps by Intervals")
stepsperInterval[stepsperInterval$steps==max(stepsperInterval$steps),"interval"]
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r maximum step, echo=TRUE}
stepsperInterval[stepsperInterval$steps==max(stepsperInterval$steps),"interval"]
```

## STEP4:Imputing missing values  

**Imputing Strategy:**I use the mean for that 5-minute interval to fill all the NA in the days.

Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r report na,echo=TRUE}
paste("There're",length(activity$steps[is.na(activity$steps)]),"NAs")
```

Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r new dataset,echo=TRUE}
activity_filled <- activity
for(i in 1:nrow(activity_filled)){
        if(is.na(activity_filled$steps[i])){
                if(i%%nrow(stepsperInterval)==0){activity_filled$steps[i] <- stepsperInterval$steps[nrow(stepsperInterval)]} else
                        activity_filled$steps[i] <- stepsperInterval$steps[i%%nrow(stepsperInterval)]
                i <- i+1
        }
}
```
Make a histogram of the total number of steps taken each day.
```{r hist fix, echo=TRUE}
totalstepsperday_filled <- aggregate(steps~date, data=activity_filled, FUN=sum, na.rm=TRUE)
hist(totalstepsperday_filled$steps, xlab="Steps per day", 
     main="Frequency of steps per day (filled dataset)")
```
Find out the Mean and Median
```{r mean med, echo=TRUE}
mean(totalstepsperday_filled$steps)
median(totalstepsperday_filled$steps)
```

## STEP5: Are there differences in activity patterns between weekdays and weekends?

Create a new factor variable in the dataset with two levels ¨C ¡°weekday¡± and ¡°weekend¡± indicating whether a given date is a weekday or weekend day. 
```{r newvec weekday, echo=TRUE}
activity_filled$day=ifelse(as.POSIXlt(as.Date(activity_filled$date))$wday%%6==0,"weekend","weekday")
activity_filled$day=factor(activity_filled$day,levels=c("weekday","weekend"))
```
Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). The plot should look something like the following, which was creating using simulated data:
```{r plot 2, echo=TRUE}
stepsInterval2=aggregate(steps~interval+day,activity_filled,mean)

library(lattice)
xyplot(steps~interval|factor(day),data=stepsInterval2,aspect=1/2,type="l")
```